### 2018-09-04 data_management.tex
Edited other docs

\vspace{2mm}
\noindent
Because of their potentially commercially sensitive nature, any data transferred between the external partners and our team will be done so in an encrypted state (whether by physical media such as USB stick or over the internet). Once on site at MFU, the raw data will immediately be backed-up on MFU's multiple backup servers. Once this has been done, raw data will be sent (via ssh, which is encrypted once the connection is established) to the UK to be backed up on Sheffield's secure servers. A Structured Query Language (SQL) database will be created to track all digital files.

\vspace{2mm}
\noindent
Once the original raw data are backed-up on both sites, work will start on researching the best means to incorporate the data into a distributed non-relational database. The data management system we will use for this is {\it Hadoop}, which is widely used throughout the IT sector, thus ensuring the long-term readability of the data. Most of our data analysis will take place within the {\it Orange} data mining software environment, which is an open-source and under constant development. These steps ensure that the data collected and produced by the project will be readable for at least 10 years.

\vspace{2mm}
\noindent
The main data that will be of use to other researchers are descriptions of the technologies we will develop to address the needs of the external partners. As with any research, our project will involve trial and error - testing different databasing and analysis techniques. The main publishable outcome of the work will be the results from these tests in terms of accuracy, reliability and speed of the database system and the ML-based analysis. By signing the Letter of Support, our external partners already have an understanding of this. Where not commercially sensitive, all raw data will be made publicly available, together with any non-commercially sensitive derived data. This includes data from Pibulsongkram Rajabhat University (User behaviour and service provision) and MFU (Academic and educational development office and M-Store).

>>>>

\vspace{2mm}
\noindent
The main risk associated with handling data from most of our external partners is their potentially commercially sensitive nature. To mitigate the risk of data loss during transfer from the partners to our servers, all data will be transferred in an encrypted state (whether by physical media such as USB stick or over the internet). Once on site at MFU, the raw data will immediately be backed-up on MFU's multiple backup servers. One of our external partners, Biophics, stands out in terms of data risk due to the sensitive medical data that they hold. Biohpics is based within the Faculty of Tropical Medicine at Mahidol University, the top ranked University within Thailand to study medicine. As such, its members of staff are extremely well-versed in Thailand's legislation surrounding the sharing of medical records. They have assured us, including within their letter of support, that all data will be fully anonymised to prevent any possible identification of individuals.

\vspace{2mm}
\noindent
Once the original raw data are backed-up, work will start on researching the best means to incorporate the data into a distributed non-relational database. The data management system we will use for this is {\it Hadoop}, which is widely used throughout the IT sector, thus ensuring the long-term readability of the data. Most of our data analysis will take place within the {\it Orange} data mining software environment, which is an open-source and under constant development. These steps ensure that the data collected and produced by the project will be readable for at least 10 years.

\vspace{2mm}
\noindent
The main data that will be of use to other researchers are descriptions of the technologies we will develop to address the needs of the external partners. As with any research, our project will involve trial and error - testing different databasing and analysis techniques. The main publishable outcome of the work will be the results from these tests in terms of accuracy, reliability and speed of the database system and the ML-based analysis. By signing the Letter of Support, our external partners already have an understanding of this. Where possible (and after full consultation with the external partners), raw data will be made publicly available, together with any non-commercially sensitive derived data.

### 2018-09-04 impact_statement.tex
Finished management plan
Edited other docs

  \vspace{3mm}
  \noindent
  {\LARGE \bf Pathways to Impact}
  %
  \vspace{3mm}
  \noindent
  The primary goals of the proposed project are to maximise the economic impact of our Newton-funded research and to build capacity within our research team to work with external businesses and organisations. The primary focus of the Newton project has been to use astronomical data give Thai data scientists and their students experience of handling and analysing significantly larger datasets than they had previously been exposed to. No Newton funds were requested to work with external partners, as we saw training as the first crucial step to our long term goal of developing home-grown talent to promote economic development in Thailand. In the process we have learned new skills and have researched novel databasing and machine learning techniques to overcome some of the challenges inherent to storing and analysing large, constantly-updated digital datasets. We now request GCRF funds to enable the students and staff to capitalise on these skills and adapt our techniques to increase the productivity of Thai businesses and organisations.

  \vspace{2mm}
  \noindent
  The GCRF project has been carefully designed to maximise impact on both our external partners as well as on team members. For the former, this corresponds to maximising productivity, while for the latter this is in the form of capacity building by getting exposure to working with external partners -- valuable experience for setting up future collaborations beyond the lifetime of the GCRF funding. Our overall strategy of working with a limited number of pre-identified external partners is based on maximising the impact of our team's {\it current} skills and techniques. In doing so, our resources will not be spread too thinly, enabling the team to gain a deep understanding of each partner's data and analysis needs, thereby ensuring the delivery of effective solutions. This strategy also ensures that there is already an understanding among the external partners that part of their role in the collaboration is to provide researchers and students a learning experience of working with outside clients. With the skills, techniques and experience our team will acquire from this project, we will apply for follow-on GCRF funding (from 2019) to support an open call to work with any eligible external partner. Beyond that, our team will have sufficient experience to become self-sustaining, thereby ensuring maximum impact over the long term.

  \vspace{2mm}
  \noindent
  As well as our overall strategy, we have also placed maximising impact at the forefront of each individual element of the workplan. By visiting the UK to present the outcome of their Newton-funded research to the GOTO collaboration, the Thai students involved in the project will gain valuable experience in communicating with -- what is to them -- their first external partner. This will be good training for working with the external partners during the GCRF project.\footnote{This visit was not budgeted-for in our Newton project as that earlier project's specific aim was to provide training in handling and analysing large datasets, not training in collaborating with external partners.} The networking event at the start of the project will enable our team to showcase our data handling/analysis skills and techniques, using GOTO as an example, while also enabling the external partners to describe the data and analysis needs and their desired outcome of the research. This will ensure that the whole team is aware of the needs of the external partners from the outset, not just the primary contact, thereby facilitating greater collaboration within the team leading to greater impact.

  \vspace{2mm}
  \noindent
  Maximising impact is also a major consideration in planning how we will work with the external partners throughout the period of the grant. From the team's own experience from collaborating on the Newton project, regular meetings are by the far the most effective means of making progress when designing data handling and analysis systems to meet a client's needs (in that case, the client was the GOTO collaboration). This is because the client has a better sense of what data fields are more important and/or informative than others, and this must be effectively communicated to the data scientists in order for them to design an effective database or analysis system. Usually, however, this is an iterative process that evolves over multiple meetings, which is why we have planned for fortnightly meetings throughout most of the period of the project. This also has the benefit of maximising team member's exposure to working with external partners -- valuable experience for building collaborations with larger numbers of businesses and organisations after this initial GCRF grant. Finally, we want to make sure that the data solutions we provide to our external partners are effective, which is why we will deliver versions of our systems at the start of month ten for Beta testing. After testing the systems for a month, we will ask our external partners to provide feedback and we will make modifications during months eleven and twelve to ensure we meet our external partners' needs by the end of the grant.

  \vspace{2mm}
  \noindent
  The research component of the project is to adapt and advance the databasing and machine-learning techniques we have developed during the Newton project to meet the needs of our external partners. An immediate, qualitative measure of the impact of this work will be in the form of the feedback that we receive from our external partners during the third networking event at the end of the project. Once the systems have been adopted by the external partners, we will be able to quantitatively measure the impact of our research and compare against expectations laid out during the first networking event. In the case of our business partners, this will be in terms of increased productivity (i.e., turnover or profit per hour worked), whereas in the case of the educational organisations this would be in terms student admissions or staff productivity. Clearly, these numbers will only become available some time after the end of the grant, but we are committed to obtaining them since the project may prove to be an eligible REF impact case study. We will, of course, forward this data to STFC for their own impact monitoring.

>>>>

  \vspace{3mm}
  \noindent
  {\LARGE \bf Pathways to Impact}

  \vspace{3mm}
  \noindent
  The primary goals of the proposed project are to expand the economic impact of our previous GCRF-funded research and to build capacity within our research team to work with a broad variety of external businesses and organisations. The primary focus of the Newton project has been to use astronomical data give Thai data scientists and their students experience of handling and analysing significantly larger datasets than they had previously been exposed to. No Newton funds were requested to work with external partners, as we saw training as the first crucial step to our long term goal of developing home-grown talent to promote economic development in Thailand. In the process we have learned new skills and have researched novel databasing and machine learning techniques to overcome some of the challenges inherent to storing and analysing large, constantly-updated digital datasets. Our follow-up GCRF Foundation Award has enabled us to work successfully with a small number of local businesses, during which we have demonstrated our ability to engage students in working with external partners. We now request follow-on GCRF funding to fully capitalise on our skills and experiences to ensure that MFU becomes a self-sustaining centre for data analytics within Thailand.

  \vspace{2mm}
  \noindent
  The GCRF project has been carefully designed to maximise impact on both our external partners as well as on team members. For the former, this corresponds to maximising productivity, while for the latter this is in the form of capacity building by getting exposure to working with external partners -- valuable experience for setting up future collaborations beyond the lifetime of the GCRF funding. Our overall strategy of working with a limited number of pre-identified external partners is based on maximising the impact of our team's {\it current} skills and techniques. In doing so, our resources will not be spread too thinly, enabling the team to gain a deep understanding of each partner's data and analysis needs, thereby ensuring the delivery of effective solutions. This strategy also ensures that there is already an understanding among the external partners that part of their role in the collaboration is to provide researchers and students a learning experience of working with outside clients.

  \vspace{2mm}
  \noindent
  As well as our overall strategy, we have also placed maximising impact at the forefront of each individual element of the workplan. The networking event at the start of the project will enable our team to showcase our data handling/analysis skills and techniques, using GOTO as an example, while also enabling the external partners to describe the data and analysis needs and their desired outcome of the research. This will ensure that the whole team is aware of the needs of the external partners from the outset, not just the primary contact, thereby facilitating greater collaboration within the team leading to greater impact.

  \vspace{2mm}
  \noindent
  Maximising impact is also a major consideration in planning how we will work with the external partners throughout the period of the grant. From the team's own experience from collaborating on our Newton and prior GCRF projects, regular meetings are by the far the most effective means of making progress when designing data handling and analysis systems to meet a client's needs. This is because the client has a better sense of what data fields are more important and/or informative than others, and this must be effectively communicated to the data scientists in order for them to design an effective database or analysis system. Usually, however, this is an iterative process that evolves over multiple meetings, which is why we have planned for fortnightly meetings throughout most of the period of the project. This also has the benefit of maximising team member's exposure to working with external partners -- valuable experience for building collaborations with larger numbers of businesses and organisations after this initial GCRF grant. Finally, we want to make sure that the data solutions we provide to our external partners are effective, which is why we will deliver versions of our systems at the start of month ten for Beta testing. After testing the systems for a month, we will ask our external partners to provide feedback and we will make modifications during months eleven and twelve to ensure we meet our external partners' needs by the end of the grant.

  \vspace{2mm}
  \noindent
  The research component of the project is to adapt and advance the databasing and machine-learning techniques we have developed so far to meet the needs of our external partners. An immediate, qualitative measure of the impact of this work will be in the form of the feedback that we receive from our external partners during the third networking event at the end of the project. Once the systems have been adopted by the external partners, we will be able to quantitatively measure the impact of our research and compare against expectations laid out during the first networking event. In the case of our business partners, this will be in terms of increased productivity (i.e., turnover or profit per hour worked), whereas in the case of the educational organisations this would be in terms student admissions or staff productivity. Clearly, these numbers will only become available some time after the end of the grant, but we are committed to obtaining them since the project may prove to be an eligible REF impact case study. We will, of course, forward this data to STFC for their own impact monitoring.

### 2018-09-04 oda_statement.tex
Edited other docs

  \vspace{2mm}
  \noindent
  Our first step in achieving our long-term goal has been to give Thai data scientists and their students experience in handling and analysing large, frequently-updated digital datasets of the kind produced by modern industries. This need was met through our Newton-funded project which gave the Thai team members access to large amounts of astronomical data. To date, this has been extremely successful; not only have the students acquired valuable training in ``Big Data'' analysis (as planned) but the team has also developed novel data handling and analysis technologies to overcome some of the challenges presented by this type of data; see our Case for Support. The next step in reaching our long-term goal is for the team to gain experience of working with external partners, which is the motivation for this, our first GCRF funding application. In researching how to adapt and develop our skills and technologies to the needs of our five external partners, we will have a real economic impact on parties external to our team. More importantly, it will prepare the team for the next step in our long-term plan: to work with a larger, more diverse range of businesses and organisations (this will form the basis of a follow-on GCRF funding application). That will give our team the experience necessary to reach our ultimate goal: to set up a self-sustaining ``Centre of Excellence'' for researching technologies to meet the data handling and analysis needs of businesses and organisations in Northern Thailand.

>>>>

  \vspace{2mm}
  \noindent
  Our first step in achieving our long-term goal has been to give Thai data scientists and their students experience in handling and analysing large, frequently-updated digital datasets of the kind produced by modern industries. This need was met through our Newton-funded project which gave the Thai team members access to large amounts of astronomical data. To date, this has been extremely successful; not only have the students acquired valuable training in ``Big Data'' analysis (as planned) but the team has also developed novel data handling and analysis technologies to overcome some of the challenges presented by this type of data; see our Case for Support. Our GCRF Foundation Award enabled our team to gain experience of working with external partners, which is already having a real economic impact on parties external to our team. We now request funding to support work with a larger, more diverse range of businesses and organisations. This will give our team the experience necessary to reach our ultimate goal: to set up a self-sustaining ``Centre of Excellence'' for researching technologies to meet the data handling and analysis needs of businesses and organisations in Northern Thailand.

### 2018-09-04 resource_justification.tex
Edited other docs

  \vspace{3mm}
  \noindent
  {\LARGE \bf Justification of resources }
  \vspace{-3mm}
  \section{Directly Incurred Costs: 20,819 (all values in GBP)}
  \vspace{-3mm}
  {\bf Networking events:} We will hold three 3-day networking events in Chiang-Rai to be attended by all co-I's, students and representatives from the external partners (up to 30 people). The first is to introduce the team to the external partners and to start to understand their needs, a second after six months to discuss and finalise broad specifications of what we will deliver, and a third at the end of the project for feedback and to explore future prospects of the partnerships. Each event is costed at 2728 and covers: hotel and flight costs for 5 participants not based in Chiang-Rai (1172), transport within Chiang-Rai (234), food and drink (970) and meeting room (352). Total: 8184. {\bf Transport to partners:} We have budgeted 773 for transport to the external partners' sites during the course of the project. {\bf User training:} We will hold a six-day workshop to train the external partners in the use of our systems. For this, we have budgeted for: meeting room (703), food and drink (646), transport (609). Total: 1959. {\bf Consumables:} We request 7500 to buy a network of five high-performance computers. This is the minimum needed to produce a working distributed database on which the external partners' data can be stored and managed effectively. On this network, we will install the {\it Hadoop} databasing ecosystem - the most widely-used solution for distributed data storage, management and analytics system - and use it to both research the optimum data storage and management solutions for our external partners and to train the end users. The network will consist of 1$\times$Hadoop cluster management module (Quad-core, 32 GB RAM; 1406), 1$\times$Database service module (Quad-core, 32 GB RAM; 1406), 1$\times$Hadoop Namenode (Quad-core, 32 GB RAM; 1406), 2$\times$Hadoop Datanodes (Quad core, 64 GB RAM each; total for both 3281). {\bf Outreach:} At the end of the project, we will host an outreach event in a public space (e.g., shopping mall) to demonstrate to the public and other businesses (i.e., potential future partners) the benefits of science in general and data science specifically. Total: 2403

  \vspace{-3mm}
  \section{Investigator Effort: 41,250}
  \vspace{-3mm}
  {\bf Thai salaries:} There are seven Thai co-Is on the grant, six of which we request 0.2FTE each. We request an extra 0.2FTE for Dr. Boongoen to account for his managerial role on the project (resulting in 0.4FTE for him). The 0.2FTE is justified on the basis that all co-I's will attend the 3-day networking events (plus 1 day each to assist with organising the events) and the six-day workshop (18 days total). Each Thai co-I is then required to commit the equivalent of 1 day per fortnight to the project (24 days). This corresponds to 0.18FTE, which we round to 0.2FTE to cover any extra time spent on the project. Total: 23598 {\bf UK FEC:} Following the same justification, we request 0.2FEC for Mullaney (salary, NI, pension, Estates, Indirect costs), of which STFC will cover 80\%. Total STFC contribution: 17652

  \vspace{-3mm}
  \section{Indirect and Estate costs at Thai Institutions: 4,720}
  \vspace{-3mm}
  As stipulated in the guide, this is calculated at a rate of 20\% of the total Thai investigator salaries.

  \vspace{-3mm}
  \section{Travel and subsistence: 6,568}
  \vspace{-3mm}
  {\bf Thai co-Is/researchers:} We request 1000 per person to cover the costs of return flights from Thailand to the UK for two research students to visit the GOTO collaboration for one week. We also request 100 per person per day for hotels and subsistence. Total: 3400 {\bf UK PI:} We request 1000 for each return flight for Mullaney to attend each networking event. Mullaney's accommodation and subsistence during the event are already included in the direct costs. Mullaney will stay for a further four nights after each event, for which we request accommodation and subsistence costs of 80 per day. Total STFC contribution (at 80\%): 3168.

  \vspace{-3mm}
  \section{Total Request: 73,357}

>>>>

  \vspace{3mm}
  \noindent
  {\LARGE \bf Justification of resources }
  \vspace{-3mm}
  \section{Directly Incurred Costs: 36,444 (all values in GBP)}
  \vspace{-3mm}
  {\bf Networking events:} We will hold four 3-day networking events in Chiang-Rai to be attended by all co-I's, students and representatives from the external partners (up to 30 people). The first is to introduce the teams to the external partners and to start to understand their needs, a second after six months to discuss and finalise broad specifications of what we will deliver. This will be repeated in year two for the new cohort of students (and any potential new partners). Each event is costed at 2851 and covers: hotel and flight costs for participants not based in Chiang-Rai (1986), transport within Chiang-Rai (230), food and drink (634). Total: 11404. {\bf Transport to partners:} We have budgeted 4468 per year for transport to and accomodation wile at the external partners' sites during the course of the project (8936 total). {\bf MOOC and Training:} Based on prior experience, we have budgeted 10,000 (covering outsourced design, filming, editing, and translating, plus web hosting) for the development of the MOOC to provide training beyond MFU students, and 3052 to hold the training workshops for people enrolled on the MOOC. For the latter, we have budgeted for: food and drink (1030), transport (919), consumables (1103). {\bf Outreach:} During the project, we will host four outreach events in publics to demonstrate to the school-age children the benefits of science in general and data science specifically. Total: 3052

  \vspace{-3mm}
  \section{Investigator Effort: XXXX}
  \vspace{-3mm}
  {\bf Thai salaries:} There are eleven Thai co-Is on the grant, for which we request 0.2FTE each. The 0.2FTE is justified on the basis that all co-I's will attend the 3-day networking events (plus 1 day each to assist with organising the events) and the four-day workshop (20 days total). Each Thai co-I is then required to commit the equivalent of 1 day per fortnight to the project (48 days). This corresponds to 0.18FTE, which we round to 0.2FTE to cover any extra time spent on the project. Total: 46,320 {\bf UK FEC:} Following the same justification, we request 0.2FEC for Mullaney (salary, NI, pension, Estates, Indirect costs), of which STFC will cover 80\%. Total STFC contribution: XXXX

  \vspace{-3mm}
  \section{Indirect and Estate costs at Thai Institutions: 9264}
  \vspace{-3mm}
  As stipulated in the guide, this is calculated at a rate of 20\% of the total Thai investigator salaries.

  \vspace{-3mm}
  \section{Travel and subsistence: 11,424}
  \vspace{-3mm}
  {\bf Thai co-Is/researchers:} We request 2000 per person to cover the costs of two return flights from Thailand to the UK for two research students to visit the GOTO collaboration for one week. We also request 100 per person per day for hotels and subsistence, and 100 per person per year for visas. Total: 7200 {\bf UK PI:} We request 1000 for each return flight for Mullaney to attend each networking event. Mullaney's accommodation and subsistence during the event are already included in the direct costs. Mullaney will stay for a further four nights after each event, for which we request accommodation and subsistence costs of 80 per day. Total STFC contribution (at 80\%): 4224.

  \vspace{-3mm}
  \section{Total Request: XXXX}
